\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2024-01-29 Articles/Article1-Conference/root.tex
added reference

Many of the recent works focus on use of a variation of artificial potential field to plan motion of the manipulator. Xia et al.~\cite{c49} uses a variation of APF for manipulator motion~\cite{c49}. Chen et al. proposes an application using APF in joint space and a variable kinematic optimization step~\cite{c50}. Long~\cite{c44} suggests creating motion plan of the manipulator using APF, he extends it using RRT to calculate virtual attractive point for the robot to move towards in case of local minima. Zhu et al. proposes use of APF in combination with MPC, to plan in environment with dynamic obstacles~\cite{c48}.

@@

ESDF grids can be generated using sensor measurements. Oleynikova et al.~\cite{oleynikova2017voxblox} proposed a method for calculating the ESDF from TSDF. Han et al.~\cite{han2019fiesta} proposed a way to integrate point-cloud data into ESDF using ray-casting.

Another way is to generate ESDF from occupancy grids. When generating ESDF from occupancy grid, common approach is the Brushfire method~\cite{lau2010improved}, that spreads from obstacles until it calculates the distance for every field on a grid. Jump Flooding Algorithm (JFA) is a similar method, that can be implemented on a GPU for faster parallel distance calculation.

@@

>>>>

Many of the recent works focus on use of a variation of artificial potential field to plan motion of the manipulator. Xia et al.~\cite{c49} uses a variation of APF for manipulator motion~\cite{c49}. Zhang et al.~\cite{zhang2021obstacle} proposes dynamic repulsive field based on direction and speed between point on robot and obstacle, it also suggests decision making force that moves the robot away from certain local minima. Chen et al. proposes\remove{ an application }using APF in joint space and a variable kinematic optimization step~\cite{c50}. Long~\cite{c44} suggests creating motion plan of the manipulator using APF, he extends it using RRT to calculate virtual attractive point for the robot to move towards in case of local minima. Zhu et al.~\cite{c48} proposes use of APF in combination with MPC, to plan in environment with dynamic obstacles.

@@

ESDF grids can be generated directly using sensor measurements. Oleynikova et al.~\cite{oleynikova2017voxblox} proposed a method for calculating the ESDF from TSDF. Han et al.~\cite{han2019fiesta} proposed a way to integrate point-cloud data into ESDF using ray-casting.

Another way is to generate ESDF from occupancy grids, that can be previously generated using sensors. When generating ESDF from occupancy grid, common approach is the Brushfire method~\cite{lau2010improved}, that spreads from obstacles until it calculates the distance for every field on a grid. Jump Flooding Algorithm (JFA) is a similar method, that can be implemented on a GPU for faster parallel distance calculation.

@@

\bibitem{zhang2021obstacle} W. Zhang, H. Cheng, L. Hao, X. Li, M. Liu, and X. Gao, “An obstacle avoidance algorithm for robot manipulators based on decision-making force,” Robotics and Computer-Integrated Manufacturing, vol. 71, p. 102114, Oct. 2021, doi: 10.1016/j.rcim.2020.102114.
